Paper 2\thanks{Code and data are available at: LINK.https://github.com/Crooksyyy/The-Effects-of-Social-Media}

### 2024-02-15 outputs/paper/paper.qmd
new graph

ggplot(cleaned_data, aes(x = reorder(hhld_inc, -table(hhld_inc)[hhld_inc]), fill = hhld_inc)) +
  geom_bar() +
  labs(x = "Household Income",
       y = "Number of Respondents") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = FALSE) # Code from Stack overflow

@@

>>>>

ggplot(cleaned_data, aes(x = reorder(hhld_inc, -table(hhld_inc)[hhld_inc]), fill = hhld_inc)) +
  geom_bar() +
  labs(x = "Household Income",
       y = "Number of Respondents") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = FALSE) # Parts of the code from Stack overflow

@@

```
```{r}
#Decrease from 12 income groups to 4 
# help from stack overflow 
#https://stackoverflow.com/questions/28190435/changing-factor-levels-with-dplyr-mutate
cleaned_data <- cleaned_data %>%
  mutate(income_group = case_when(
    hhld_inc %in% c("$0 to $9,999", "$10,000 to $19,999") ~ "$0 to $19,999",
    hhld_inc %in% c("$20,000 to $29,999", "$30,000 to $39,999", "$40,000 to $49,999") ~ "$20,000 to $49,999",
    hhld_inc %in% c("$50,000 to $59,999", "$60,000 to $74,999", "$75,000 to $99,999") ~ "$50,000 to $99,999",
    hhld_inc %in% c("$100,000 to $124,999", "$125,000 to $149,999", "$150,000 and up") ~ "$100,000 and up",
    TRUE ~ "Prefer not to answer"
  ))

ggplot(cleaned_data, aes(x = follow_trump, fill = income_group)) +
  geom_bar(position = 'stack', color = 'black', stat = 'count') +
  labs(title = "Number of People Following Trump by Income Group",
       x = "Follows Trump",
       y = "Count") +
  scale_fill_manual(values = c(
    "$0 to $19,999" = 'lightblue',
    "$20,000 to $49,999" = 'lightcoral',
    "$50,000 to $99,999" = 'lightgreen',
    "$100,000 and up" = 'plum',
    "Unknown or Prefer not to answer" = 'lightgrey'
  )) +
  theme_minimal()

### 2024-02-15 outputs/paper/paper.tex
new graph

>>>>

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#Decrease from 12 income groups to 4 }
\CommentTok{\# help from stack overflow }
\CommentTok{\#https://stackoverflow.com/questions/28190435/changing{-}factor{-}levels{-}with{-}dplyr{-}mutate}
\NormalTok{cleaned\_data }\OtherTok{\textless{}{-}}\NormalTok{ cleaned\_data }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{income\_group =} \FunctionTok{case\_when}\NormalTok{(}
\NormalTok{    hhld\_inc }\SpecialCharTok{\%in\%} \FunctionTok{c}\NormalTok{(}\StringTok{"$0 to $9,999"}\NormalTok{, }\StringTok{"$10,000 to $19,999"}\NormalTok{) }\SpecialCharTok{\textasciitilde{}} \StringTok{"$0 to $19,999"}\NormalTok{,}
\NormalTok{    hhld\_inc }\SpecialCharTok{\%in\%} \FunctionTok{c}\NormalTok{(}\StringTok{"$20,000 to $29,999"}\NormalTok{, }\StringTok{"$30,000 to $39,999"}\NormalTok{, }\StringTok{"$40,000 to $49,999"}\NormalTok{) }\SpecialCharTok{\textasciitilde{}} \StringTok{"$20,000 to $49,999"}\NormalTok{,}
\NormalTok{    hhld\_inc }\SpecialCharTok{\%in\%} \FunctionTok{c}\NormalTok{(}\StringTok{"$50,000 to $59,999"}\NormalTok{, }\StringTok{"$60,000 to $74,999"}\NormalTok{, }\StringTok{"$75,000 to $99,999"}\NormalTok{) }\SpecialCharTok{\textasciitilde{}} \StringTok{"$50,000 to $99,999"}\NormalTok{,}
\NormalTok{    hhld\_inc }\SpecialCharTok{\%in\%} \FunctionTok{c}\NormalTok{(}\StringTok{"$100,000 to $124,999"}\NormalTok{, }\StringTok{"$125,000 to $149,999"}\NormalTok{, }\StringTok{"$150,000 and up"}\NormalTok{) }\SpecialCharTok{\textasciitilde{}} \StringTok{"$100,000 and up"}\NormalTok{,}
    \ConstantTok{TRUE} \SpecialCharTok{\textasciitilde{}} \StringTok{"Prefer not to answer"}
\NormalTok{  ))}

\FunctionTok{ggplot}\NormalTok{(cleaned\_data, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ follow\_trump, }\AttributeTok{fill =}\NormalTok{ income\_group)) }\SpecialCharTok{+}
  \FunctionTok{geom\_bar}\NormalTok{(}\AttributeTok{position =} \StringTok{\textquotesingle{}stack\textquotesingle{}}\NormalTok{, }\AttributeTok{color =} \StringTok{\textquotesingle{}black\textquotesingle{}}\NormalTok{, }\AttributeTok{stat =} \StringTok{\textquotesingle{}count\textquotesingle{}}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Number of People Following Trump by Income Group"}\NormalTok{,}
       \AttributeTok{x =} \StringTok{"Follows Trump"}\NormalTok{,}
       \AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_fill\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}
    \StringTok{"$0 to $19,999"} \OtherTok{=} \StringTok{\textquotesingle{}lightblue\textquotesingle{}}\NormalTok{,}
    \StringTok{"$20,000 to $49,999"} \OtherTok{=} \StringTok{\textquotesingle{}lightcoral\textquotesingle{}}\NormalTok{,}
    \StringTok{"$50,000 to $99,999"} \OtherTok{=} \StringTok{\textquotesingle{}lightgreen\textquotesingle{}}\NormalTok{,}
    \StringTok{"$100,000 and up"} \OtherTok{=} \StringTok{\textquotesingle{}plum\textquotesingle{}}\NormalTok{,}
    \StringTok{"Unknown or Prefer not to answer"} \OtherTok{=} \StringTok{\textquotesingle{}lightgrey\textquotesingle{}}
\NormalTok{  )) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\includegraphics{paper_files/figure-pdf/unnamed-chunk-6-1.pdf}
